---
title: "Proposal: Seminars' series weekly overview"
author: "Cesar Herrera"
date: "October 2017"
output: 
  html_document:
    self_contained: false
    mathjax: null

---
<head>
  <style type="text/css">
    body {
    background-color: #FFFFF0;
    }
    .main-container{
    max-width: 700px;
    width: auto;
    margin: auto;
    padding: 1em; 
    background-color: #FFEFD5;
    }
    img{
    -ms-interpolation-mode:bicubic;
    }
  </style>
</head>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(knitr.kanle.NA = ' ')

```



***********
<img src="https://egrs.jcu.edu.au/Members/jc306494/seminar-series/researh_seminars_series_banner/at_download/file" alt="James Cook University - Seminar Series" width="700">


#<span style="color:red; font-family:Georgia; font-size:1em;">Seminar series weekly overview.</span>
<http://www.jcu.edu.au/seminarseries>


```{r echo=FALSE}
seminars_files <- list.files(pattern=".csv$")
list.seminars <- list()

for (i in 1:length(seminars_files)) {
  list.seminars[[i]] <- read.csv(seminars_files[i], colClasses = rep("character",23))
}

names(list.seminars) <- seminars_files

empty_img <- "https://egrs.jcu.edu.au/Members/jc306494/seminar-series/empty_image_seminars_series/at_download/file"
list.seminars[[1]][1,21:23] <- lapply(list.seminars[[1]][1,21:23], function(x) {x[x==""] <- empty_img;x})
list.seminars[[2]][1,21:23] <- lapply(list.seminars[[2]][1,21:23], function(x) {x[x==""] <- empty_img;x})
list.seminars[[3]][1,21:23] <- lapply(list.seminars[[3]][1,21:23], function(x) {x[x==""] <- empty_img;x})
list.seminars[[4]][1,21:23] <- lapply(list.seminars[[4]][1,21:23], function(x) {x[x==""] <- empty_img;x})
#list.seminars <-lapply(list.seminars, function(x) {x[is.na(x)] <- "";x})

```


Seminar               |                    |   Place  |
------------                    |----                   | ------------------------      | --------------------
**<span style="color:blue">`r list.seminars[[1]][1,1]`</span>**     | `r list.seminars[[1]][1,2]` (`r list.seminars[[1]][1,3]`)     | `r list.seminars[[1]][1,4]` | <a href="`r list.seminars[[1]][1,5]`"> <img src="`r list.seminars[[1]][1,7]`" width="200"> </a>
**<span style="color:blue">`r list.seminars[[2]][1,1]`</span>**     | `r list.seminars[[2]][1,2]` (`r list.seminars[[2]][1,3]`)  | `r list.seminars[[2]][1,4]` | <a href="`r list.seminars[[2]][1,5]`"> <img src="`r list.seminars[[2]][1,7]`" width="200"> </a>
**<span style="color:blue">`r list.seminars[[3]][1,1]`</span>**     | `r list.seminars[[3]][1,2]` (`r list.seminars[[3]][1,3]`) |  `r list.seminars[[3]][1,4]` | [`r list.seminars[[3]][1,7]`](`r list.seminars[[3]][1,5]`)
**<span style="color:blue">`r list.seminars[[4]][1,1]`</span>**     | `r list.seminars[[4]][1,2]` (`r list.seminars[[4]][1,3]`)  | `r list.seminars[[4]][1,4]` | <a href="`r list.seminars[[4]][1,5]`"> <img src="`r list.seminars[[4]][1,7]`" width="200"> </a>


#<span style="color:red; font-family:Georgia; font-size:1em;">This week:</span>

***********

###**<span style="color:blue">`r list.seminars[[1]][1,1]`</span>**

####<u>**`r list.seminars[[1]][1,9]`**</u>
<font size="4" color="black">`r list.seminars[[1]][1,12]`</font> <font size="2" color="dimgray"><b>`r list.seminars[[1]][1,15]`</b></font></p>
<font size="4" color="black">`r list.seminars[[1]][1,13]`</font> <font size="2" color="dimgray"><b>`r list.seminars[[1]][1,16]`</b></font></p>
<font size="4" color="black">`r list.seminars[[1]][1,14]`</font> <font size="2" color="dimgray"><b>`r list.seminars[[1]][1,17]`</b></font></p>


**Abstract:**

`r list.seminars[[1]][1,10]`

`r list.seminars[[1]][1,11]`


<p><img src="`r list.seminars[[1]][1,21]`" alt="" align="left" onerror="this.style.display='none'"/>`r list.seminars[[1]][1,18]`</p> <BR CLEAR="LEFT">

<p><img src="`r list.seminars[[1]][1,22]`" alt="" align="left">`r list.seminars[[1]][1,19]`</p> <BR CLEAR="LEFT">

<p><img src="`r list.seminars[[1]][1,23]`" alt="" align="left">`r list.seminars[[1]][1,20]`</p> <BR CLEAR="LEFT">

`r list.seminars[[1]][1,8]`

**<span style="color:blue">`r list.seminars[[1]][1,2]` `r list.seminars[[1]][1,3]`**

**<span style="color:blue">`r list.seminars[[1]][1,4]`**

Find more at [`r list.seminars[[1]][1,5]`](`r list.seminars[[1]][1,5]`)

Enquiries: [`r list.seminars[[1]][1,6]`]

***********

###**<span style="color:blue">`r list.seminars[[2]][1,1]`</span>**

####<u>**`r list.seminars[[2]][1,9]`**</u>
<font size="4" color="black">`r list.seminars[[2]][1,12]`</font> <font size="2" color="dimgray"><b>`r list.seminars[[2]][1,15]`</b></font></p>
<font size="4" color="black">`r list.seminars[[2]][1,13]`</font> <font size="2" color="dimgray"><b>`r list.seminars[[2]][1,16]`</b></font></p>
<font size="4" color="black">`r list.seminars[[2]][1,14]`</font> <font size="2" color="dimgray"><b>`r list.seminars[[2]][1,17]`</b></font></p>


**Abstract:**

`r list.seminars[[2]][1,10]`

`r list.seminars[[2]][1,11]`

<p><img src="`r list.seminars[[2]][1,21]`" alt=""  align="left">`r list.seminars[[2]][1,18]`</p> <BR CLEAR="LEFT">

<p><img src="`r list.seminars[[2]][1,22]`" alt=""  align="left">`r list.seminars[[2]][1,19]`</p> <BR CLEAR="LEFT">

<p><img src="`r list.seminars[[2]][1,23]`" alt=""  align="left">`r list.seminars[[2]][1,20]`</p> <BR CLEAR="LEFT">


`r list.seminars[[2]][1,8]`

**<span style="color:blue">`r list.seminars[[2]][1,2]` `r list.seminars[[2]][1,3]`**

**<span style="color:blue">`r list.seminars[[2]][1,4]`**

Find more at [`r list.seminars[[2]][1,5]`](`r list.seminars[[2]][1,5]`)

Enquiries: [`r list.seminars[[2]][1,6]`]

***********

###**<span style="color:blue">`r list.seminars[[3]][1,1]`</span>**

####<u>**`r list.seminars[[3]][1,9]`**</u>
<font size="4" color="black">`r list.seminars[[3]][1,12]`</font> <font size="2" color="dimgray"><b>`r list.seminars[[3]][1,15]`</b></font></p>
<font size="4" color="black">`r list.seminars[[3]][1,13]`</font> <font size="2" color="dimgray"><b>`r list.seminars[[3]][1,16]`</b></font></p>
<font size="4" color="black">`r list.seminars[[3]][1,14]`</font> <font size="2" color="dimgray"><b>`r list.seminars[[3]][1,17]`</b></font></p>


**Abstract:**

`r list.seminars[[3]][1,10]`

`r list.seminars[[3]][1,11]`


<p><img src="`r list.seminars[[3]][1,21]`" alt=""  align="left">`r list.seminars[[3]][1,18]`</p> <BR CLEAR="LEFT">

<p><img src="`r list.seminars[[3]][1,22]`" alt=""  align="left">`r list.seminars[[3]][1,19]`</p> <BR CLEAR="LEFT">

<p><img src="`r list.seminars[[3]][1,23]`" alt=""  align="left">`r list.seminars[[3]][1,20]`</p> <BR CLEAR="LEFT">

`r list.seminars[[3]][1,8]`

**<span style="color:blue">`r list.seminars[[3]][1,2]` `r list.seminars[[3]][1,3]`**

**<span style="color:blue">`r list.seminars[[3]][1,4]`**

Find more at [`r list.seminars[[3]][1,5]`](`r list.seminars[[3]][1,5]`)

Enquiries: [`r list.seminars[[3]][1,6]`]

***********

###**<span style="color:blue">`r list.seminars[[4]][1,1]`</span>**

####<u>**`r list.seminars[[4]][1,9]`**</u>
<font size="4" color="black">`r list.seminars[[4]][1,12]`</font> <font size="2" color="dimgray"><b>`r list.seminars[[4]][1,15]`</b></font></p>
<font size="4" color="black">`r list.seminars[[4]][1,13]`</font> <font size="2" color="dimgray"><b>`r list.seminars[[4]][1,16]`</b></font></p>
<font size="4" color="black">`r list.seminars[[4]][1,14]`</font> <font size="2" color="dimgray"><b>`r list.seminars[[4]][1,17]`</b></font></p>


**Abstract:**

`r list.seminars[[4]][1,10]`

`r list.seminars[[4]][1,11]`


<p><img src="`r list.seminars[[4]][1,21]`" alt=""  align="left">`r list.seminars[[4]][1,18]`</p> <BR CLEAR="LEFT">

<p><img src="`r list.seminars[[4]][1,22]`" alt=""  align="left">`r list.seminars[[4]][1,19]`</p> <BR CLEAR="LEFT">

<p><img src="`r list.seminars[[4]][1,23]`" alt=""  align="left">`r list.seminars[[4]][1,20]`</p> <BR CLEAR="LEFT">

`r list.seminars[[4]][1,8]`

**<span style="color:blue">`r list.seminars[[4]][1,2]` `r list.seminars[[4]][1,3]`**

**<span style="color:blue">`r list.seminars[[4]][1,4]`**

Find more at [`r list.seminars[[4]][1,5]`](`r list.seminars[[4]][1,5]`)

Enquiries: [`r list.seminars[[4]][1,6]`]
